\date{}
\documentclass{scrartcl}
\usepackage{cv}
\usepackage{graphicx}

%----------------------------------------

\begin{document}

\pagestyle{empty} % Stop the page count at the bottom of the first page

\setlength{\hoffset}{4em}
\setlength{\voffset}{2em}

%----------------------------------------
%  NAME AND CONTACT INFORMATION SECTION
%----------------------------------------

\begin{cv}{\spacedallcaps{Mateusz Kubuszok}}\vspace{1.5em}

\noindent\SecHeader{Personal Information}

\NewEntry{email}{}{\href{mailto:mateusz.kubuszok@gmail.com}{mateusz.kubuszok@gmail.com}}

\NewEntry{website}{}{\href{https://kubuszok.com/}{https://kubuszok.com/}}

\NewEntry{GitHub}{}{\href{https://github.com/MateuszKubuszok/}{https://github.com/MateuszKubuszok/}}

\NewEntry{Linked.in}{}{\href{https://linkedin.com/in/mateuszkubuszok/}{https://linkedin.com/in/mateuszkubuszok/}}

\vspace{1em}

%----------------------------------------
%  WORK EXPERIENCE
%----------------------------------------

\noindent\SecHeader{Work Experience}

%----------------------------------------

\NewEntry{Oct,\,2020--Feb,\,2023}{Senior BE Developer}{, \textsc{SwissBorg} --- Żory (remote)}

\Description{\MarginText{SwissBorg SA} \textsc{Scala}. Backend Developer: Scala, Cats Effect, Akka Typed, Akka Stream, Akka Cluster, Kafka, Protobufs. Developed advertizing app (CryptoChallenge) backend, co-architected critical service, developed internal tools and DX enhancements based on metaprogramming.}

%----------------------------------------

\NewEntry{Aug,\,2018--Nov,\,2019}{Senior BE Developer}{, \textsc{Coya} --- Wrocław (remote)}

\Description{\MarginText{Coya AG} \textsc{Scala}. Backend Developer: Scala, Monix, Doobie, AWS Kinesis,
AWS DynamoDB, Akka Streams, Akka HTTP. Contributed to architecture designing and planning, made internal
Scala and FP workshops. Domain Driven Design.}

%----------------------------------------

\NewEntry{Feb,\,2018--Jul,\,2018}{BE Developer}{, \textsc{Order Metrics} --- Wrocław (remote)}

\Description{\MarginText{Order Metrics Inc.} \textsc{Scala}. Working as a backend developer: REST, running scheduled tasks, migations. Occasionally small frontend tasks. Play Framework, Akka Stream, Monix, Slick, FlywayDB, PostgreSQL, sbt, node, React + Redux, Heroku, AWS (EC2).}

%----------------------------------------

\NewEntry{Mar,\,2017--Jan,\,2018}{CTO, BE Developer}{, \textsc{Skillhouse.io} --- Wrocław}

\Description{\MarginText{Skilhouse.io} \textsc{Scala}. Internally, working as a backend developer and an architect: developed whole backend and designed REST API for frontend. Externally, acting as a CTO. Akka HTTP, Akka Stream, Cats, Monix, Slick, FlywayDB, sbt, PostgreSQL, AWS (EBS, RDS).}

%----------------------------------------

\NewEntry{Jun,\,2015--Jul,\,2017}{Scala Developer}{, \textsc{ScalaC} --- Wrocław (remote)}

\Description{\MarginText{ScalaC} \textsc{Scala}. Working as Scala consultant. Contributed to development of e-commerce and fintech applications. Akka HTTP, Play Framework, Slick, MariaDB, ElasticSearch, sbt.}

%----------------------------------------

\NewEntry{Mar,\,2014--May,\,2015}{Developer}{, \textsc{Opera Software} --- Wrocław}

\Description{\MarginText{Opera Software ASA} \textsc{C++}. Working on desktop version of company's flag product, Opera browser. Chromium, GYP.}

%----------------------------------------

\NewEntry{Oct,\,2012--Jul,\,2013}{Intern}{, \textsc{Nokia Siemens Networks} --- Wrocław}

\Description{\MarginText{Nokia Siemens Networks} \textsc{Java SE/EE}. Participated in work on internal dimensioning tool. Introduced autoupdater to said project's default update tool. Guava, Guice, Gradle.}

%----------------------------------------

\newpage

\NewEntry{Jun,\,2012}{Intern}{, \textsc{PGS Software} --- Wrocław}

\Description{\MarginText{PGS Software} \textsc{Java EE}. Worked on server application built with Spring Framework, Hibernate and jQuery technologies.}

%----------------------------------------

\NewEntry{Feb,\,2012--Jul,\,2012}{Developer}{, Academic Project --- Wrocław}

\Description{\MarginText{Academic Project} \textsc{Java EE}. Developed repository for a generic software updater. Project overviewed by Nokia Siemens Networks.}

%----------------------------------------
%  EDUCATION
%----------------------------------------

\SecHeader{Education}

%----------------------------------------

\NewEntry{2013--2014}{Wrocław University of Technology}{, Wrocław}

\Description{\MarginText{Master of Science}GPA: 4.0\ \ \Dot\ \ \textit{Algorithmics}\ \ \Dot\ \ Faculty of Fundamental Problem of Technology\newline 
Thesis: \textit{\Highlight{Tools for calculating Nash equlibria in finite games}}\newline
Description: This thesis concerned creation of equlibria-calculating tools and algorithms used to find them.}

%----------------------------------------

\NewEntry{2009--2013}{Wrocław University of Technology}{, Wrocław}

\Description{\MarginText{Bachelor of Science}GPA: 4.5\ \ \Dot\ \ Faculty of Fundamental Problem of Technology\newline 
Thesis: \textit{\Highlight{Client of autoupdater server}}\newline
Description: This thesis concerned creation of a generic updater client.}

%----------------------------------------
%  OTHER ACHEIEVEMENTS
%----------------------------------------

\SecHeader{Other achievements}

%----------------------------------------

\NewEntry{eBook}{\href{https://leanpub.com/jvm-scala-book/}{\small Things you need to know about JVM}}{}

\Description{\MarginText{Publications}An introduction to JVM, GC, byte-code and how it affects Scala language.}

%----------------------------------------

\NewEntry{Blog}{\href{https://kubuszok.com/}{Kubuszok.com}}{}

\Description{\MarginText{Publications}Writing in-depth articles about Scala and functional programming.}

%----------------------------------------

\NewEntry{Scala libraries}{\href{https://scalaland.io/}{Scalaland.io}}{}

\Description{\MarginText{Open Source}Coauthoring a set of various utilities for Scala language, among others data-transformation library \href{https://scalalandio.github.io/chimney/}{Chimney} (over 1000 stars on GitHub).}

%----------------------------------------

\NewEntry{Meetups and conferences}{\href{https://kubuszok.com/presentations}{Prelections and workshops about Scala}}{}

\Description{\MarginText{Prelections}Made prelections on meetups (London Functional Programmers, Functional Tricity, ScalaWAW, Kraków JUG) and conferences (Scalar, Lambda Days), as well as workshops (ScalaWave, Lambda Days) on Scala and Scala libraries.}

%----------------------------------------

\NewEntry{Knowledge sharing}{\href{https://stackoverflow.com/users/1305121/mateusz-kubuszok}{Active StackOverflow member}}{}

\Description{\MarginText{StackOverflow}Gained over 25000 reputation by helping other community members solve their techinical issues.}

%----------------------------------------

\vspace{0.5em}

%----------------------------------------
%  OTHER INFORMATION
%----------------------------------------

\SecHeader{Other Information}

%----------------------------------------

\newlength{\langbox}
\settowidth{\langbox}{English}

%----------------------------------------

\Description{\MarginText{Languages}\parbox{\langbox}{\textsc{Polish}}\ \ \Dot\ \ \ Mother tongue}

\vspace{-0.5em}

\Description{\parbox{\langbox}{\textsc{English}}\ \ \Dot\ \ \ Advanced (professional proficiency)}

\vspace{-0.5em}

%----------------------------------------

\Description{\MarginText{Interests}Computer Science\ \ \Dot\ \ Comparative religion\ \ \Dot\ \ Hiking\ \ \Dot\ \ Running\ \ \Dot\ \ Cycling}

%----------------------------------------

\end{cv}

\tiny{I hereby declare that all the facts and information for this cover letter and CV are true. I allow my personal data stated in the abovemnetioned applications to be processed for the purpose of recruitment, in accordance with the Personal Data Protection Act dated 29/08/1997 (Dz. Ust. No. 133, item 883)}

\end{document}